Eurovision Song Contest: semifinal 1, 2009

### 2022-07-14 inst/eurovision.Rmd
more work

print(a$year)

bloc <- function(lam){
  out <- hyper3()
  e <- list2ec(l)
  for(y in unique(a$year)){
     v <- a$country[a$year==y]
     ec <- e[names(e) %in% v]
     out <- out + cheering3(v=v, e=ec,h=rep(lam,length(unique(e))))
   } 
  return(out)
}

Ha <- bloc(1.888)
Hb <- bloc(1.9)
```

Now maximize it:

```{r,maxbloc,cache=TRUE}
maxp(Ha,n=2,give=TRUE)
maxp(Hb,n=2,give=TRUE)
```

```{r,maxhelp,cache=TRUE}
o <- function(lam){
   H <- bloc(lam)
   return(maxp(Hb,give=TRUE,n=1)$likes)
}

o(1)
o(2)

lam <- seq(from=0.6,to=1.5,len=4)
```

>>>>

bloc <- function(lam){
  out <- hyper3()
  e <- list2ec(l)
  for(y in unique(a$year)){
     v <- a$country[a$year==y]
     ec <- e[names(e) %in% v]
     out <- out + cheering3(v=v, e=ec,h=rep(lam,length(unique(e))))
   } 
  return(out)
}
```

```{r,defineoptimand}
o <- function(lam){  # maximize function o()
   H <- bloc(lam)
   return(maxp(H,give=TRUE,n=1)$likes)
}

```{r,maximi,cache=TRUE}
lam <- seq(from=0.5,to=2,len=10)
L <- sapply(lam,o)
```

```{r,plotmaximi}
plot(lam,L-max(L),type="b",pch=16)
```
